---
title       : Prevent Heart Disease
subtitle    : Assess the probability of having a Coronary Heart Disease
author      : Cristian Mastrofrancesco
job         : statistician
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : prettify  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## CHD

* We have built a risk assessment tool for estimating
a person 10-year risk of having a heart attack

* Heart disease has been the leading cause of death
worldwide

* Risk factors are variables that increase the chances of a
disease

* Key to successful prediction of CHD: identifying the most
important risk factors


---

## Risk factors

We took into account different features:
+ demographic
+ behavioral
+ medical history
+ last blood test results

---

## Cholesterol and CHD


```{r echo = F, results = 'asis'}
require(rCharts)
load("framingham.Rdata") 

dataset = as.data.frame(prop.table(table(framingham$TenYearCHD, framingham$cholBins),2))
colnames(dataset)=c("CHD", "Cholesterol", "Frequency")
n1 = nPlot(Frequency ~ Cholesterol,  group = "CHD", data = dataset, type = "multiBarChart")
n1$print("chart1")

```

Cholesterol is a dangerous risk factor!


---

## Smoking behavior and CHD

```{r echo = F, results = 'asis'}
require(rCharts)
load("framingham.Rdata") 

dataset = as.data.frame(prop.table(table(framingham$TenYearCHD, framingham$smokerclass),2))
colnames(dataset)=c("CHD", "Smoker", "Frequency")
n1 = nPlot(Frequency ~ Smoker,  group = "CHD", data = dataset, type = "multiBarChart")
n1$print("chart2")

```

Smoking doesn't seem to be so dangerous regarding CHD

---

## Glucose levels and CHD

```{r echo = F, results = 'asis'}
require(rCharts)
load("framingham.Rdata") 

dataset = as.data.frame(prop.table(table(framingham$TenYearCHD, framingham$glucoseclass),2))
colnames(dataset)=c("CHD", "Glucose", "Frequency")
n1 = nPlot(Frequency ~ Glucose,  group = "CHD", data = dataset, type = "multiBarChart")
n1$print("chart3")

```

Glucose levels have an high impact on the probability a person has a CHD!!!

---

## Weight and CHD

```{r echo = F, results = 'asis'}
require(rCharts)
load("framingham.Rdata") 

dataset = as.data.frame(prop.table(table(framingham$TenYearCHD, framingham$weightclass),2))
colnames(dataset)=c("CHD", "Weight", "Frequency")
n1 = nPlot(Frequency ~ Weight,  group = "CHD", data = dataset, type = "multiBarChart")
n1$print("chart4")

```

Also weight has a strong impact on the probaiblity to have a CHD!!

---

## Modeling CHD

We use logistic regression on training set to predict
whether or not a patient experienced CHD within 10
years of first examination.

The model can differentiate low-risk from high-risk
patients.
